From Freebase to Wikidata: The Great Migration

### 2016-01-29 paper.tex
Added a subsection on the motivation for the shutdown and on Freebase's future.

>>>>

\subsection{Motivation for the Migration}

When Google publicly launched Freebase back in 2007, Freebase was thought of as a ``Wikipedia for structured data''.
The Knowledge Graph team at Google have been closely watching the Wikimedia Foundation's project Wikidata since its launch,
and believe strongly in a robust community-driven effort to collect and curate structured knowledge about the world.
The team now think they can serve that goal best by supporting Wikidata, as the project is growing fast,
has an active community, and is better-suited to lead an open collaborative knowledge base~\cite{freebase2014shutdown}.

In consequence, in mid-2015, the Freebase service as a standalone project was wound down.
Freebase always has supported developer access to the data;
in order to still cater for this need,
a~new API for entity search powered by Google's Knowledge Graph was launched.%
\footnote{Knowledge Graph Search API: \url{https://developers.google.com/knowledge-graph/?hl=en}}
Freebase has as of March 31, 2015, gone read-only, \emph{i.e.},
the website no longer accepts edits and the MQL write API was retired.
